\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-31 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
changes to preamble of section 5

	\textcolor{red}{GA: I will rewrite/review this when we decide where we put all our results - I am referring to the projection results - currently I think it is best that everything goes here and we make a comment at the end of Section 3.3 guiding the reader to the results here. This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.} Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice. Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}). However, our motivation in this study is to demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.

>>>>

	\textcolor{red}{GA: I will rewrite/review this when we decide where we put all our results - I am referring to the projection results - currently I think it is best that everything goes here and we make a comment at the end of Section 3.3 guiding the reader to the results here. This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.} Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice. Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}). However, our motivation in this study is twofold.  First, we demonstrate the implications of Theorem~\ref{th:distred} by comparing reconciled and base forecasts and in contrast to previous studies we consider individual periods rather than computing averages over a rolling window.  The second, we demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.
